With the [leaflet package](https://r-graph-gallery.com/package/leaflet.html), it is easy to include an interactive map into a quarto document.

```{r package_load, message=FALSE}
pacman::p_load(here, leaflet)
here::i_am("images_in_R_plots.qmd")
```

# First map

This example is taken from their [documentation](https://rstudio.github.io/leaflet/articles/leaflet.html).


```{r}
m <- leaflet()
m <- addTiles(m)
m <- addMarkers(m, lng=174.768, lat=-36.852, popup="The birthplace of R")
m
```


# Let's find SLU on the map

First we render a map of the entire world.

```{r}
library(leaflet)
m <- leaflet() %>% addTiles()
m  # a map with the default OSM tile layer
```

            [32.958984, -5.353521], // [lng, lat] - southwestern corner of the bounds
            [43.50585, 5.615985] // [lng, lat] - northeastern corner of the bounds
Then we hone in on Sweden. The coordinates here are in the format `(longitude east, latitude south, longitude west, latitude north)`. 

```{r}
m %>% fitBounds(15, 55, 17, 70)
```